### 2016-04-01 docs/ms_communitySynchrony.Rmd
fixers typo in growth rate prediction equations
adds text to ms on percent cover results

\begin{equation}
\phi_{R,\mathcal{M}_{E}} = \frac{\sum_{i,j}p_ip_j\text{cov}(u_{ei},u_{ej})}{S^2}
\end{equation}

@@

For all five communities, the synchrony of species' growth rates in monoculture almost perfectly matched species synchrony in polyculture (Fig. 3).
Results for synchrony of percent cover are qualitatively similar, but simulation results were more variable and less consistent with analytical predictions and observed synchrony (Figs. S2-S3).

DISCUSSION
----------
Our study produced four main findings that were generally consistent across five natural plant communities: (1) limiting-case predictions from the theoretical model were well-supported by simulations from the empirical models; (2) demographic stochasticity decreased community synchrony, as expected by theory, and its effect was largest in small populations; (3) environmental fluctuations increased community synchrony relative to simulations in constant environments because species-specific responses to the environment were positively, though not perfectly, correlated; and (4) interspecific interactions were weak and therefore had little impact on community synchrony.
We also found that analyses based on synchrony of species' percent cover were uninformative (Figs. S2-S3), implying that it is difficult to decipher mechanisms of species synchrony from abundance time series, as expected by theory [@Loreau2008a].

>>>>

\begin{equation}
\phi_{R,\mathcal{M}_{E}} = \frac{\sum_{i,j}\text{cov}(u_{ei},u_{ej})}{S^2}
\end{equation}

@@

For all five communities, the synchrony of species' growth rates in monoculture almost perfectly matched species synchrony in polyculture (Fig. 3).
Results for synchrony of percent cover are qualitatively similar, but simulation results were more variable and less consistent with analytical predictions and observed synchrony (Online Supporting Information, Figs. S2-S3).

DISCUSSION
----------
Our study produced four main findings that were generally consistent across five natural plant communities: (1) limiting-case predictions from the theoretical model were well-supported by simulations from the empirical models; (2) demographic stochasticity decreased community synchrony, as expected by theory, and its effect was largest in small populations; (3) environmental fluctuations increased community synchrony relative to simulations in constant environments because species-specific responses to the environment were positively, though not perfectly, correlated; and (4) interspecific interactions were weak and therefore had little impact on community synchrony.
We also found that analyses based on synchrony of species' percent cover, rather than growth rates, were uninformative (Figs. S2-S3) since the linear approximation required for analytical predictions is a stronger assumption for abundance than growth rates, especially given relatively short time-series (Online Supporting Information).
Thus, our results provide further evidence that it is difficult to decipher mechanisms of species synchrony from abundance time series, as expected by theory [@Loreau2008a].

### 2016-04-01 docs/ms_communitySynchrony.tex
fixers typo in growth rate prediction equations
adds text to ms on percent cover results

For all five communities, the synchrony of species' growth rates in
monoculture almost perfectly matched species synchrony in polyculture
(Fig. 3). Results for synchrony of percent cover are qualitatively
similar, but simulation results were more variable and less consistent
with analytical predictions and observed synchrony (Figs. S2-S3).

@@

Our study produced four main findings that were generally consistent
across five natural plant communities: (1) limiting-case predictions
from the theoretical model were well-supported by simulations from the
empirical models; (2) demographic stochasticity decreased community
synchrony, as expected by theory, and its effect was largest in small
populations; (3) environmental fluctuations increased community
synchrony relative to simulations in constant environments because
species-specific responses to the environment were positively, though
not perfectly, correlated; and (4) interspecific interactions were weak
and therefore had little impact on community synchrony. We also found
that analyses based on synchrony of species' percent cover were
uninformative (Figs. S2-S3), implying that it is difficult to decipher
mechanisms of species synchrony from abundance time series, as expected
by theory (Loreau and {{de Mazancourt}} 2008).

@@

Loreau, M. 2010. From Polutations to Ecosystems: Theoretical Fondations
for a New Ecological Synthesis.

@@

Vellend, M., L. Baeten, I. H. Myers-Smith, S. C. Elmendorf, R.
Beauséjour, C. D. Brown, P. {De Frenne}, K. Verheyen, and S. Wipf. 2013.
Global meta-analysis reveals no net change in local-scale plant
biodiversity over time. Proceedings of the National Academy of Sciences
of the United States of America 110:19456--9.

>>>>

For all five communities, the synchrony of species' growth rates in
monoculture almost perfectly matched species synchrony in polyculture
(Fig. 3). Results for synchrony of percent cover are qualitatively
similar, but simulation results were more variable and less consistent
with analytical predictions and observed synchrony (Online Supporting
Information, Figs. S2-S3).

@@

Our study produced four main findings that were generally consistent
across five natural plant communities: (1) limiting-case predictions
from the theoretical model were well-supported by simulations from the
empirical models; (2) demographic stochasticity decreased community
synchrony, as expected by theory, and its effect was largest in small
populations; (3) environmental fluctuations increased community
synchrony relative to simulations in constant environments because
species-specific responses to the environment were positively, though
not perfectly, correlated; and (4) interspecific interactions were weak
and therefore had little impact on community synchrony. We also found
that analyses based on synchrony of species' percent cover, rather than
growth rates, were uninformative (Figs. S2-S3) since the linear
approximation required for analytical predictions is a stronger
assumption for abundance than growth rates, especially given relatively
short time-series (Online Supporting Information). Thus, our results
provide further evidence that it is difficult to decipher mechanisms of
species synchrony from abundance time series, as expected by theory
(Loreau and {{de Mazancourt}} 2008).

@@

Loreau, M. 2010. From Populations to Ecosystems: Theoretical Fondations
for a New Ecological Synthesis.

@@

Vellend, M., L. Baeten, I. H. Myers-Smith, S. C. Elmendorf, R.
Beaus{é}jour, C. D. Brown, P. {De Frenne}, K. Verheyen, and S. Wipf.
2013. Global meta-analysis reveals no net change in local-scale plant
biodiversity over time. Proceedings of the National Academy of Sciences
of the United States of America 110:19456--9.
